Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-10-03 Manuscript/manuscriptPSsuppl.tex
Add figure showing the effect of two different concentration definitions to the changes of headgroup order parameters Figure and data contibuted by Ricky Nencini by email.

>>>>

\pagebreak
\section{Effect of the definition of concentration on the headgroup order parameters as a function of ion concentration.}\label{concentrationDEFfigure}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/OP_ECC_POPC_DPPC_water_conc2_dppc_bulk.pdf}
  \caption{\label{concentrationDEFfigure}
    Difference between order parameter changes as a function of CaCl$_2$ concentration demonstrated
    for the two possible definitions of ion concentration, concentration in buffer before solvating the
    lipids (buffer concentration) and concenrtration in bulk after solvating the lipids (bulk concentration) \cite{melcr18}. 
}
\end{figure}
